\section{
  \IfLanguageName{portuguese}%
    {Skills}
    {Skills}
  }
  \vspace{3pt}
  \resumeSubHeadingListStart

    \resumeSubheading
      {%
        \IfLanguageName{portuguese}%
          {Linguagens}
          {Languages}
      }{}
      {%
        \IfLanguageName{portuguese}%
          {Shell Script, Python, PHP, Ruby. Aprendendo GoLang e Java (SpringBoot).}
          {Shell Script, Python, PHP, Ruby. Learning GoLang and Java (SpringBoot).}
      }{}

    \resumeSubheading
      {%
        \IfLanguageName{portuguese}%
          {Infraestrutura como Código}
          {Infrastructure as Code}
      }{}
      {%
        {Terraform, CloudFormation.}
      }{}

    \resumeSubheading
      {%
        \IfLanguageName{portuguese}%
          {Gerenciamento de Configuração}
          {Configuration Management}
      }{}
      {%
        {Ansible, Puppet.}
      }{}

    \resumeSubheading
      {%
        \IfLanguageName{portuguese}%
          {Orquestração e Containers}
          {Orchestration and Containers}
      }{}
      {%
        {Docker, Docker Compose, Elastic Kubernetes Service (EKS), Kubernetes on-premise, Elastic Container Service (ECS).}
      }{}

    \resumeSubheading
      {%
        \IfLanguageName{portuguese}%
          {Integração Contínua(CI)}
          {Continuous Integration (CI)}
      }{}
      {%
        {Gitlab, Github, CodePipeline, Bamboo, CodeCommit, CodeBuild, CodePipeline.}
      }{}

    \resumeSubheading
      {%
        \IfLanguageName{portuguese}%
          {Entrega Contínua}
          {Continuous Deployment/Delivery}
      }{}
      {%
        {ArgoCD, Bamboo, CodeDeploy, Gitlab, Github Actions, CodeDeploy.}
      }{}

    \resumeSubheading
      {%
        \IfLanguageName{portuguese}%
          {Provedores Cloud}
          {Cloud Providers}
      }{}
      {%
        {Amazon Web Services (AWS).}
      }{}

    \resumeSubheading
      {%
        \IfLanguageName{portuguese}%
          {Monitoramento e Logs}
          {Monitoring and Logs}
      }{}
      {%
        {Grafana, Cloudwatch, Jaeger, Loki, ELK Stack.}
      }{}


  \resumeSubHeadingListEnd
